\documentclass[preparation.tex]{subfiles}
\begin{document}
\section{Data Preparation} % (fold)
\label{sec:preparation}
Before modelling, the data obtained from SteamSpy had to be cleansed and
modified to better suit the problem being investigated.

The AppID and Name fields were irrelevant, simply being IDs rather than actual
data. Therefore, it was ideal that they be removed from the dataset during the
modelling process.

\subsection{Categorising Score \& Price} % (fold)
\label{sub:categorising_score_price}
The goal of the project is to create a model for estimating the ScoreRank
field. Thus, it maybe better to try and predict the score as a range, rather
than the specific value. In order to address this, additional columns were made
for `ScoreGrade' and `PriceBand'. ScoreGrade divides the ScoreRanks into ten
different grades, based on its score from 0-10, 10-20 and so on. This matches
up with the histogram shown in \fullref{fig:score_rank}.

The same principle was applied with PriceBand, which maps each price to a \$5
denomination. It should again be pointed out how this makes the lowest band
inflate in size to the number of free-to-play games in the dataset. It may be
ideal for this to be its own price band, rather than being merged with the paid
games less than \$5.
% subsection categorising_score_price (end)

\subsection{Owners, Players, Playtime} % (fold)
\label{sub:owners_players_playtime}
For owners and players, a continuous field does not seem appropriate for the
task at hand. It is unlikely that a difference of 500 owners will make an
impact on any resulting model. As such, an additional field will be created by
turning the continuous values into ranges. These three fields will be cut into
groups at intervals of every half million. It is likely that a more appropriate
figure may be found during the modelling process. Playtime will be converted
from minutes into hours using similar methods. Half an hour periods may be used
if it is found to be more appropriate.
% subsection owners_players_playtime (end)

\subsection{Tags} % (fold)
\label{sub:tags}
It was decided that only tags present in many games should be focused on, with
tags that only appear in a few games being ignored. Any tag that was present in
under 20 games was removed, leaving 29 of the 200 tags originally in the
dataset.
% subsection tags (end)
% section preparation (end)
\end{document}